### 2021-01-04 ch02_scientific_background/scientific_background.tex
Added section on ESMValTool
Added subsection on calculation of CRE feedback parameters

Due to the complex nature of the Earth system itself, numerical models of it
consist of hundreds of thousands of lines of computer code. Thus, a
standardization to a certain degree is crucial for the various research groups
developing \acp{ESM} all around the world in order to obtain comparable output
and to facilitate model analysis. For this reason, the \ac{WGCM} of the
\ac{WCRP} initiated the \ac{CMIP} in 1995, with the objective to
\enquote{better understand past, present and future climate changes arising
  from natural, unforced variability or in response to changes in radiative
  forcing in a multi-model context} \autocite{WCRP2020}. One major element of
\ac{CMIP} is to establish common standards, coordination, infrastructure and
documentation in order to facilitate the distribution of climate model output
\autocite{Eyring2016}.

@@

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\FigureWidth{}]{
    ch02_scientific_background/figs/keeling_curve.pdf}
  \caption{The Keeling Curve: monthly-mean atmospheric \acs{CO2} concentration
    at the Mauna Loa Observatory, Hawaii ($19.5 \unit{\degree N}$, $155.6
    \unit{\degree W}$; elevation: $3397 \unit{m}$) from 1958 to 2019
    \autocite{Keeling2005}. The steady increase of the atmospheric \acs{CO2}
    concentration is superimposed with a seasonal oscillation caused by the
    seasonal \acs{CO2} cycle (see \cref{subsec:02:carbon_cycle_overview}).}
  \label{fig:02:keeling_curve}
\end{figure}

>>>>

Due to the complex nature of the Earth system itself, numerical models of it
consist of hundreds of thousands of lines of computer code. Thus, a
standardization to a certain degree is crucial for the various research groups
developing \acp{ESM} all around the world in order to obtain comparable output
and to facilitate model analysis. For this reason, the \ac{WGCM} of the
\ac{WCRP} initiated the \ac{CMIP} in 1995, with the objective to
\enquote{better understand past, present and future climate changes arising
  from natural, unforced variability or in response to changes in radiative
  forcing in a multi-model context} \autocite{WCRP2020}. One major element of
\ac{CMIP} is to establish common standards, coordination, infrastructure and
documentation in order to facilitate the distribution of climate model output
\autocite{Eyring2016, Juckes2020}.

@@

\subsection{Cloud-Related Feedback Parameters}
\label{subsec:02:cloud_feedback_parameters}

In addition to the calculation of the external forcing $F$, the overall climate
feedback parameter $\lambda$ and the \ac{ECS}, the Gregory regression can also
be used to estimate cloud-related feedback parameters. For this, the net
\ac{TOA} radiation $N$ on the y-axis in \cref{fig:02:gregory_regression} is
replaced with the \ac{CRE}, which is defined as the difference between the
all-sky (\ie{} with clouds if present) net \ac{TOA} radiation and the clear-sky
(\ie{} clouds artificially removed) net \ac{TOA} radiation
\autocite{Andrews2012}. This can be done for the shortwave $N_\text{SWCRE}$ and
longwave $N_\text{LWCRE}$ components separately, but also for the combined
effect $N_\text{CRE} = N_\text{SWCRE} + N_\text{LWCRE}$. The slopes in the
corresponding Gregory regressions are the so-called \emph{\ac{CRE} feedback
  parameters} $\lambda_\text{SWCRE}$, $\lambda_\text{LWCRE}$ and
$\lambda_\text{CRE}$, which quantify the change in \ac{CRE} as a response to
increasing \acp{GSAT}.

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\LargeFigureWidth{}]{
    ch02_scientific_background/figs/keeling_curve.pdf}
  \caption{The Keeling Curve: monthly-mean atmospheric \acs{CO2} concentration
    at the Mauna Loa Observatory, Hawaii ($19.5 \unit{\degree N}$, $155.6
    \unit{\degree W}$; elevation: $3397 \unit{m}$) from 1958 to 2019
    \autocite{Keeling2005}. The steady increase of the atmospheric \acs{CO2}
    concentration is superimposed with a seasonal oscillation caused by the
    seasonal \acs{CO2} cycle (see \cref{subsec:02:carbon_cycle_overview}).}
  \label{fig:02:keeling_curve}
\end{figure}
